FATE summary results

### 2019-12-15 paper draft.Rmd
Calculated proportion of loadings above and below 0

@@

```{r, echo=F}
all <- readRDS("all_plankton_12.11.19.one.trend.rds") 
all$summary
```

@@

>>>>

# and look at the proportion of posteriors > or < 0 for each era
for(i in 2:4){
x <- mod[,i]
print(names(mod)[i])
print(paste("Proportion < 0: ", sum(x < 0)/length(x)))
print(paste("Proportion > 0: ", sum(x > 0)/length(x)))
}

@@

```{r, echo=F}
# all <- readRDS("all_plankton_12.11.19.one.trend.rds") 
all <- readRDS("GOA_plankton_11.18.19.one.trends.rds") 
all$summary
```

@@

# and look at the proportion of posteriors > or < 0

x <- mod[,2]
print(names(mod)[i])
print(paste("Proportion < 0: ", sum(x < 0)/length(x)))
print(paste("Proportion > 0: ", sum(x > 0)/length(x)))
